|

### 2023-06-14 presentations/2023-colloque-montreal.qmd
Revisions to colloque presentation after comments from BMR

---
title: |
    | Profiling 
    | the 15-min *ped shed* 
    | from the perspective of 
    | network attributes
author: "**Antonio Páez**, Belén Martín, Josh Arbess, James R. Dunn"
format: revealjs
execute: 
  cache: true
---

@@

- A form of chronourbanism that emphasizes movement at a human scale;
- in environments that accommodate a wide range of capabilities throughout the lifespan;
- and with the aim of improving livability and health.

@@

The 15-min neighborhood^[Sometimes mislabeled as the 15-min city.] is powered by:

::: {.r-fit-text style="margin-top: 50px; font-size: 3em; color: black;"}
The 15-min ped shed
:::

@@

When combined with the environment, the 15-min ped shed is:

@@

$$
A_i = \sum_{j \in \text{15-min ped shed}} O_j
$$

Keeping the environment constant, bigger ped sheds result in higher accessibility.

@@

The maximum ped shed area^[For a given walking speed] would be in a homogeneous, isotropic surface (i.e., a featureless plain)

@@

Streetscapes limit where movement can happen, which inevitably leads to smaller ped sheds.

@@

How much do 15-min ped sheds vary in a typical Canadian city (Hamilton)?

@@

Open source data

@@

Open source software (`R`)

@@

Open, reproducible research

@@

# Ped sheds

@@

Ped sheds calculated from zonal centroids using [`r5r`](https://ipeagit.github.io/r5r/) assuming a walking speed of 3.6 $km/h$.

@@

ggplot() +
  geom_sf(data = sample_net,
          color = "lightgray") +
  geom_sf(data = sample_da,
          fill = NA,
          linewidth = 1,
          color = "#619CFF") +
  geom_sf(data = sample_da_coords,
          color = "#619CFF",
          size = 3) +
  annotation_scale() +

  theme_void()
```

@@

Summary of ped shed areas (max. ped shed area is `r round(pi * max_shed_r^2 |> units::set_units(km^2), 2)` $km^2$).

@@

Profiling the ped sheds based on their network attributes.

@@

# Network attributes of ped sheds

@@

Re-examining the areas of the ped sheds.

@@

Ped shed area as a function of network attributes.

@@

- Ped shed area varies greatly within Hamilton.
- The size of ped sheds varies significantly with the attributes of the network.
- The effect is non-linear.
- Results suggest an optimal combination of attributes to maximize ped shed areas.

@@

- Typically suburban networks result in relatively small ped sheds.
- Turning suburbs into 15-min neighborhoods may require major transportation infrastructure changes.
- Alternatively, major increases in density.

@@

- Expand the analysis to include the environment, i.e., the opportunity landscape.

>>>>

---
title: |
    | Profiling 
    | the 15-min *pedshed* 
    | from the perspective of 
    | network attributes
author: "**Antonio Páez**, Belén Martín, Josh Arbess, James R. Dunn"
format: revealjs
execute: 
  cache: true
---

@@

The 15-min neighborhood^[Sometimes mislabeled as the 15-min city.].

- A form of chronourbanism that emphasizes movement at a human scale...
- ...in environments that accommodate a wide range of capabilities throughout the lifespan...
- ...with the aim of improving livability and health.

@@

The 15-min neighborhood is powered by:

::: {.r-fit-text style="margin-top: 50px; font-size: 3em; color: black;"}
The 15-min pedshed
:::

@@

When combined with the environment, the 15-min pedshed is:

@@

$$
A_i = \sum_{j \in \text{15-min pedshed}} O_j
$$

Keeping the environment constant, bigger pedsheds result in higher accessibility.

@@

The maximum pedshed area^[For a given walking speed] would be in a homogeneous, isotropic surface (i.e., a featureless plain).

@@

Streetscapes limit where movement can happen, which inevitably leads to smaller pedsheds.

@@

How much do 15-min pedsheds vary in a typical Canadian city (Hamilton)?

@@

Open source data.

@@

Open source software (`R`).

@@

Open, reproducible research.

@@

# pedsheds

@@

pedsheds calculated from zonal centroids using [`r5r`](https://ipeagit.github.io/r5r/) assuming a walking speed of 3.6 $km/h$.

@@

ggplot() +
  geom_sf(data = sample_net,
          color = "lightgray") +
  geom_sf(data = sample_da,
          fill = NA,
          linewidth = 1,
          color = "#619CFF") +
  geom_sf(data = sample_da_coords,
          color = "#619CFF",
          size = 3) +
  geom_sf(data = sample_da_coords |>
            st_buffer(dist = 900),
          fill = NA,
          color = "black") +
  labs(caption = "Blue polygon is DA boundary; blue dot is centroid") +
  annotation_scale() +
  theme_void()
```

@@

Summary of pedshed areas (max. pedshed area is `r round(pi * max_shed_r^2 |> units::set_units(km^2), 2)` $km^2$).

@@

Profiling the pedsheds based on their network attributes.

@@

# Network attributes of pedsheds

@@

Re-examining the areas of the pedsheds.

@@

pedshed area as a function of network attributes.

@@

- pedshed area varies greatly within Hamilton.
- The size of pedsheds varies significantly with the attributes of the network.
- The effect is non-linear.
- Results suggest an optimal combination of attributes to maximize pedshed areas.

@@

- Typically suburban networks result in relatively small pedsheds.
- Turning suburbs into 15-min neighborhoods may require major transportation infrastructure changes.
- Alternatively, major increases in density.
- Very unlikely that the 15-min city will be achieved, but many 15-min neighborhoods may be possible.

@@

- Expand the analysis to include the environment, i.e., the opportunity landscape.
- Try other cities.
